Ribosome accumulation during early phase resistance training

### 2020-08-27 manuscript.Rmd
Figure 1 complete draft

---
title: "Ribosome accumulation during early phase resistance training"
author: Daniel Hammarström^1,2,£^&ast;,Sjur Øfsteng^2,£^  Bent R. Rønnestad^2^, Stian Ellefsen^1,3^
date: ""
header-includes:
  - \usepackage{wasysym}
csl: resources/experimental-physiology.csl
bibliography: resources/bibliography.bib
output:
  word_document:
    reference_docx: resources/manuscript_word_template.docx
editor_options: 
  chunk_output_type: console
---
<!-- This is a comment  -->
<!-- Add comments after each reference for tracking (eg[@RN2364]<!-- comment -->
<!-- After references, add a row break without space (this will put the reference on the end on the line). -->

@@

# Results

>>>>

---
title: "Ribosome accumulation during early phase resistance training"
author: Daniel Hammarström^1,2,£^&ast;,Sjur Øfsteng^2,£^, Lise Koll^3^,   Bent R. Rønnestad^2^, Stian Ellefsen^1,3^
date: ""
header-includes:
  - \usepackage{wasysym}
csl: resources/experimental-physiology.csl
bibliography: resources/bibliography.bib
output:
  word_document:
    reference_docx: resources/manuscript_word_template.docx
editor_options: 
  chunk_output_type: console
---
<!-- This is a comment  -->
<!-- Add comments after each reference for tracking (eg[@RN2364]<!-- comment -->
<!-- After references, add a row break without space (this will put the reference on the end on the line). -->

@@

# Results
```{r training-data}

load.stats <- read_excel("./data/tr010_training.xlsx", sheet = 1, na = "NA") %>%
  inner_join(read_excel("./data/leg_randomization.xlsx")) %>%
  filter(exercise == "legext") %>%
  mutate(set.load = repetitions * load, 
         week = if_else(session %in% c(1:4), "W1", if_else(session %in% c(5:8), "W2", "W3"))) %>%
  group_by(participant, cond, session, week) %>%
  summarise(load = mean(load, na.rm = TRUE)) %>%
  mutate(week = factor(week, levels = c("W1", "W2", "W3"))) %>%
  print()

load.m1 <- lme(log(load) ~ week + week:cond, random = list(participant = ~1), 
               data = load.stats, method = "ML")
load.m0 <- lme(log(load) ~ week, random = list(participant = ~1), 
               data = load.stats, method = "ML")

load.anova <- anova(load.m0, load.m1)

load.intervals <- data.frame(exp(intervals(load.m0)$fixed) - 1)

load.inr.w2 <- paste0(sprintf("%.0f",load.intervals[2, 2]*100), 
                      "%, 95% CI: [",
                      sprintf("%.0f",load.intervals[2, 1]*100), 
                      ", ",
                      sprintf("%.0f",load.intervals[2, 3]*100), 
                      "]")
load.inr.w3 <- paste0(sprintf("%.0f",load.intervals[3, 2]*100), 
                      "%, 95% CI: [",
                      sprintf("%.0f",load.intervals[3, 1]*100), 
                      ", ",
                      sprintf("%.0f",load.intervals[3, 3]*100), 
                      "]")

All participants successfully completed their prescribed sessions. The different training protocols resulted in diverging loading profiles (load &#215; repetitions) over the course of the study (Figure 1B). The intensity of exercise (load at 10RM) increased similarly in both conditions from the first to the second (`r load.inr.w2`) and third (`r load.inr.w3`)  four-session block, respectively. Compared to the non-training control group, isokinetic strength increased to Session 12 in the experimental group, with an attenuated difference seen after de-training (Figure 1C). Average isometric strength showed the same general pattern although with considerable more uncertainty indicated by wider 95% CI (Figure 1C). Muscle thickness of the *m. vastus lateralis* increased in the experimental group compared to the control group both after Session 12 and after eight days of de-training (Figure 1D). There were no indications of differences between training conditions in strength or muscle thickness changes.
